Automated Topic Naming

### 2012-01-17 ese/ese.tex
R2 fixes in section 4.3

By contrast, the PostgreSQL time-line  (Figure \ref{fig:pgsql-timeline}) is extracted from a central trunk and is not version-specific. Therefore development 
tends to be focused on releases 7.3, 7.4 and 7.5/8.0 alpha. For example, a priority for the 8.0 candidate was a Windows-native port of the source code, which seems to 
correlate with the \emph{portability} NFR increasing in frequency in mid-2004. Before the 7.4 release, \emph{usability,functionality} and \emph{portability} all 
increase in frequency, possibly reflecting the interest in adding features and documentation for the release.

In the following sections we turn to our research questions:

@@

We wanted to see how similar developers were to each other in terms of
the NFRs that worked on. 
Within this section we focused on PostgreSQL.
First we did pairwise $X^2$ (chi-squared)
tests and Kolmogorov-Smirnov tests for each developer pair and we
found that $3/10$ of these tests the developers were significantly
different, that is their distributions were not similar. This implies
that there are authors who focus on different NFRs or different
proportion of NFRs.

@@

It should be noted that much of PostgreSQL development originates from
the mailinglist and the developers are often pushing integrations. If
we compare the global NFR distribution to each author we find that 1
quarter of the authors have a similarity of $0.47$ or less. This is
depicted in Figure \ref{fig:authorsim} where we can see that not all
authors are as similar to the global trend as others. Of course, we
found that number of commits correlated with an author's similarity to the
global NFR distribution ($0.59$ Pearson).

@@

Given the top 15 PostgreSQL developers we found that proportionally many
developers had a focus on NFR topics. Authors with top proportions per NFR
were:
\texttt{dennis} for usability; 
\texttt{scrappy} and \texttt{meskes} for portability;
\texttt{inoue} and \texttt{neilc} for efficiency;
\texttt{jurka} and \texttt{joe} for reliability;
\texttt{thomas} and \texttt{weick} for functionality;
and \texttt{ishii} and \texttt{scrappy} for maintainability.
Given these results we found that yes indeed there was often a focus
of $1/3$ to $1/10$ of commits dedicated to a particular NFR.

>>>>

By contrast, the PostgreSQL time-line  (Figure \ref{fig:pgsql-timeline}) is extracted from a central trunk and is not version-specific. Therefore development 
tends to be focused on releases 7.3, 7.4 and 7.5/8.0 alpha. For example, a priority for the 8.0 candidate was a Windows-native port of the source code, which seems to 
correlate with the \emph{portability} NFR increasing in frequency in mid-2004. Before the 7.4 release, \emph{usability,functionality} and \emph{portability} all 
increase in frequency, possibly reflecting the interest in adding features and documentation for the release. In the following sections we turn to our research questions:

@@

We wanted to see how similar developers were to each other in terms of
the NFRs that they worked on. 
Within this section we focused on PostgreSQL.
We first conducted pairwise $X^2$ (chi-squared)
tests and Kolmogorov-Smirnov tests for each developer pair. We
found that in $3/10$ of these tests, the developers were significantly
different, i.e., their distributions were not similar. This implies
that there are authors who focus on different NFRs or different
proportion of NFRs.

@@

It should be noted that much of PostgreSQL development originates from
the mailinglist and the developers are often pushing integrations. If
we compare the global NFR distribution to each author we find that 25\%
 of the authors have a similarity of $0.47$ or less. This is
depicted in Figure \ref{fig:authorsim}, where we can see that not all
authors are as similar to the global trend as others. Of course, we
found that number of commits correlated with an author's similarity to the
global NFR distribution ($0.59$ Pearson).

@@

Given the top 15 PostgreSQL developers we found that proportionally many
developers had a focus on NFR topics. Authors with top proportions per NFR
were:
\texttt{dennis} for usability; 
\texttt{scrappy} and \texttt{meskes} for portability;
\texttt{inoue} and \texttt{neilc} for efficiency;
\texttt{jurka} and \texttt{joe} for reliability;
\texttt{thomas} and \texttt{weick} for functionality;
and \texttt{ishii} and \texttt{scrappy} for maintainability.
Given these results we found that there indeed was a focus
of $1/3$ to $1/10$ of commits dedicated to a particular NFR.
